---
title: "Exercices"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Basic R Exercises
 
#### Understanding and Fixing Code
  
- Fix the part of the code that shows the cold months in Baltimore so we know which are those months.
  
```{r}
months <- c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec")
tempLo <- c(23.5,26.1,33.6,42.0,51.8,60.8,65.8,63.9,56.6,43.7,34.7,27.3)
tooCold <- (((5/9) * (tempLo - 32)) < 0)
tooCold
```

Show the months:

```{r}
names(tooCold) <- months
tooCold
```

- What would happen if we still had a NA on the vector for the temperatures in SJC?

  Problems with some operators.

- What	happens	if	we	try	to	run	sjcTemps["Jan":"Jul",c(1,3)]?	Why?

```{r}
maxTempSJC <- c(29.7,30.1,29.5,27.3,25.1,24.3,24.1,26.2,27.2,27.3,28,28.7)
avgTempSJC <- c(22.2,22.4,21.6,19.6,17,16.1,15.6,17.1,18.8,19.4,20.3,21.4)
minTempSJC <- c(16.2,16.5,15.7,13.2,10.1,8.9,8.2,9.9,11.9,13.4,14.2,15.3)
months <- c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec")
sjcTemps <- data.frame(Max=maxTempSJC,Avg=avgTempSJC,Min=minTempSJC,row.names = months)
sjcTemps
```

  An error occurred: _Error in "Jan":"Jul" : Argumento NA/NaN_

- We can change Data Frames with sjcTemps3["Aug",] <- c(1,2,3) and sjcTemps3["Jul",] <- sjcTemps3["Jul",]+c(3,4) but we cannot	change with	sjcTemps3["Jul",] <- c(3,4).	Why?

  Replacement has 2 items, need 3

- Run	some	examples	that	show	that	the	recycling	rule reuses	the	smaller	(shorter) vector

- What does stringsAsFactors=FALSE in read.csv() do? Why do we need it?

To avoid problems delay re-encoding of strings by using stringsAsFactors = FALSE when creating data.frames

#### Baltimore Rainfall

The	average	monthly	rainfall	in	Baltimore	is,	in	inches:
3.47,	3.02, 3.93,	3.00,	3.89,	3.43,	3.85,	3.74,	3.98,	3.16,	3.12,	3.35

Write	an	R	program	that	shows	this	in	millimeters	(one	inch	=	25.4	mm),	add	names	to	the	
vector,	and	calculates its	average,	minimum and	maximum

```{r}
avgBaltimore <- c(3.47,	3.02, 3.93,	3.00,	3.89,	3.43,	3.85,	3.74,	3.98,	3.16,	3.12,	3.35)
```

```{r}
avgBaltimore <- avgBaltimore * 24.5
avgBaltimore
```

```{r}
months <- c("Jan","Feb","Mar","Apr","May","Jun","Jul","Aug","Sep","Oct","Nov","Dec")
names(avgBaltimore) <- months
avgBaltimore
```



#### Tidy Data: The “hotdog” variable for the “Hot Dogs in Baltimore” example can be better defined.

#### Tidy Data: I prefer Pizza
 
#### Tidy Data: Get the name of the town for the “Hot Dogs in Baltimore” example

#### Tidy Data: Complete the Codebook for the “Hot Dogs in Baltimore” example
